---
title: "Package Tutorial"
author: "Logan Kelley"
date: "2023-11-19"
output: html_document
---

#An Introduction to My R Package

This R packages helps users process data sets in specific ways. The package has functions for removing NA's from your data set, mutating a weight column in units of grams into a column in the units of kilograms, create a summary of a linear model with a responder and predictor, create a scatter plot comparing two columns in your data frame, and creating a summary of min, max, and mean of a column in the data frame. 

#Installing the R package

To install this R package enter the following code into your console. 

```{r, eval=False}
install.packages("remotes")
library(remotes)

install.packages("googlesheets4")
library(googlesheets4)

remotes::install_github("CR4WDAD/kelley.pkg")
```

#Downloading Data for Package 

To download the data set for this package enter the following code:

```{r, eval=False, include=TRUE}
googlesheets4::gs4_deauth()
surveys <- read_sheet("https://docs.google.com/spreadsheets/d/1if1TIUxvCg3LtR0deHq1NgXPNOSMo0Wt4JhirsN0JBE/edit?usp=sharing")
```

#Functions in This Package and How to Use Them

There are five functions in this Package. This section of the tutorial will go through how to use each one and why. 

##Remove NA's
##Mutate grams to kilograms
##Linear Model
##Scatter Plot 
##Min, Max, Mean