---
title: "Package Tutorial"
author: "Logan Kelley"
date: "2023-11-19"
output: html_document
---

#An Introduction to My R Package

This R packages helps users process data sets in specific ways. The package has functions for removing NA's from your data set, mutating a weight column in units of grams into a column in the units of kilograms, create a summary of a linear model with a responder and predictor, create a scatter plot comparing two columns in your data frame, and creating a summary of min, max, and mean of a column in the data frame. 

#Installing the R package

To install this R package enter the following code into your console. 

```{r, eval=False,include = TRUE}
install.packages("remotes")
library(remotes)

install.packages("googlesheets4")
library(googlesheets4)

remotes::install_github("CR4WDAD/kelley.pkg")
```

#Downloading Data for Package 

To download the data set for this package enter the following code:

```{r, eval=False, include=TRUE}
googlesheets4::gs4_deauth()
surveys <- read_sheet("https://docs.google.com/spreadsheets/d/1if1TIUxvCg3LtR0deHq1NgXPNOSMo0Wt4JhirsN0JBE/edit?usp=sharing")
```

#Functions in This Package and How to Use Them

There are five functions in this Package. This section of the tutorial will go through how to use each one and why. 

##Remove NA's
The first function in this package is used to clean data. It removes NA's from all the columns in the data frame. The name of this function is remove_nas(). 
Enter this code in your console:
```{r}
remove_nas(surveys)
```
If everything worked properly the data-set should be clear of all NAs

##Mutate grams to kilograms
The second function in this package is used to convert a weight column from the unit grams to the unit kilograms. The name of this function is mutation().
Enter this code in your console:
```{r}
mutation(surveys, species_id, weight)
```
If everything worked properly the data-set should have a new column called "weight_kg" with the correct conversion
##Linear Model
The third function in this package is used to create a summary of a linear model to see if a predictor has an effect on the response. The name of this function is lm_function().
Enter this code in your console: 
```{r}
lm_function(surveys, "weight", "hindfoot_length")
```
If everything worked properly you should see a linear model summary that indicates weight is in fact a predictor of hindfoot_length
##Scatter Plot 
The fourth function in this package is used to create a scatter plot of 2 columns in your data set. The name of this function is plot_graph().
Enter this code in your console:
```{r}
plot_graph(surveys, weight, hindfoot_length)
```
If everything worked properly a scatter plot with weight on the x-axis and hindfoot_length on the y-axis should be generated. 
##Min, Max, Mean
The fifth and final function in this package is used to create a summary of the min, max, and mean of a column. The name of this function is tm().
Enter this code in your console:
```{r}
tm(surveys, weight, sex)

```
If everything worked properly a summary of the minimum, maximum, and mean weight of both sexes should be displayed. 